---
title: "RMedlineFunctions Examples 'myasthenia gravis'"
output: html_notebook
---

This is a first attempt at building an example of RMedlineFunctions (https://github.com/fdsayre/RMedlineFunctions) using an RNoteBook to display some results.

This example uses 'Myasthenia Gravis' as a search query. There is a fair amount of research on Myasthenia Gravis, so some parts of the script, such as adding data about citations, can take a long time to complete. 

A shorter example looking at 'librarian[ti]' is in the works.


Load functions and libraries

```{r}
source("RMedlineFunctions.R")
library(RISmed)
library(ggplot2)
library(dplyr)
library(rworldmap)

```

Set query (can be anything you would search in pubmed.gov)
retrieve medline data file

the first variable sets the first year you want results from (2000), the second the last year (2016), and the third the maximum number of results to return.

The turn that medline data file into a data frame with most article metadata (but not all!)

```{r}
query = 'myasthenia gravis'
data <- RetrieveArticleData(query,2000,2016,30000)
article_metadata <- RetrieveMostArticleMetadata(data)
```


Let's take a quick look at how pubmed translated that query

```{r}
Query(data)
```


Create a basic bar chart shorting publication frequency by year from article metadata file (must contain at least a Year variable)

```{r}
ArticlesFreqYear(article_metadata)
```

Plot article status using medline data file

```{r}
PMStatusByYearPlot(data)
```


Get data on number of times each article has been cited and add that data to an existing article metadata file.

WARNING: CITATION DATA TAKES A LONG TIME TO COLLECT

variables for function:
x = medline data file
y = article metadata file that has PMIDs


```{r}
article_metadata_citations <- GetCitationData(data, article_metadata)
```

Plot citations for each paper as a scatterplot (each dot is independent)

```{r}
PlotCitations(article_metadata_citations)
```

Bar graph of culumative citations by year
This is really the total number of citations, so not incredibly useful

```{r}
PlotCitationsBar(article_metadata_citations)
```

Do some mapping (here, later move this into a seperate function)

Map prep
# NEED TO CHANGE ARTICLE METADATA from line 90 to something unique so as to not override that

```{r}
data_country_frame <- data.frame("ID"=ArticleId(data),"Country"=Country(data))
article_metadata <- merge(article_metadata_citations, data_country_frame, by="ID")

maping_base_data <- article_metadata %>%
  select(Year, Country, ID, values) %>%
  group_by(Country) %>%
  summarise(totalcites = sum(values))

malMap <- joinCountryData2Map(maping_base_data, joinCode = "NAME", nameJoinColumn = "Country", verbose = TRUE)

```

Fix some names

```{r}
maping_base_data$Country[maping_base_data$Country=="England"] <- "United Kingdom"

maping_base_data$Country[maping_base_data$Country=="China (Republic : 1949- )"] <- "China"
```

Re-run to generate malmap

```{r}
malMap <- joinCountryData2Map(maping_base_data, joinCode = "NAME", nameJoinColumn = "Country", verbose = TRUE)
```

Still some names not working but lets map things anyway

```{r}
mapCountryData(malMap, nameColumnToPlot="totalcites", catMethod = "pretty", missingCountryCol = gray(.8), colourPalette = "heat")
```

