---
title: "RMedlineFunctions Examples 'reproducibility'"
output: html_notebook
---

This is an example of the RMedlineFunctions (https://github.com/fdsayre/RMedlineFunctions) I'm building to extend the functionality of the RISmed R package. 

This example uses 'reproducibility[ti] or reproducible[ti]' as a search query in Pubmed. 

These functions are in very early development and not everything (a) works, and (b) is coherent. With things like mapping I am still more focused on learning how to manipulate and display data than I necessarily am on creating a coherent rational analysis.


Load functions and libraries

```{r}
source("RMedlineFunctions.R")
library(RISmed)
library(ggplot2)
library(dplyr)
library(rworldmap)

```

Set query (can be anything you would search in pubmed.gov)
retrieve medline data file

the first variable sets the first year you want results from (2000), the second the last year (2016), and the third the maximum number of results to return.

The turn that medline data file into a data frame with most article metadata (but not all!)

```{r}
query = 'reproducibility[ti]'
data <- RetrieveArticleData(query,2000,2016,50000)
article_metadata <- RetrieveMostArticleMetadata(data)
```


Let's take a quick look at how pubmed translated that query

```{r}
Query(data)
```


Create a basic bar chart shorting publication frequency by year from article metadata file (must contain at least a Year variable)

```{r}
ArticlesFreqYear(article_metadata)
```

Plot article status using medline data file

```{r}
PMStatusByYearPlot(data)
```


Let's look at the MeSH most used in this set and then use head to look at the first rows. There will be lots of NAs from non-indexed sources and it won't be sorted in any order

```{r}
MeSH <- GetMeSH(data)
head(MeSH)
```

Now lets filter for just MeSH descriptors (not qualifiers yet) and sort in decending order

```{r}
CountedMesh <- CountMeSH(MeSH)
head(CountedMesh)
```


Get data on number of times each article has been cited and add that data to an existing article metadata file.

WARNING: CITATION DATA TAKES A LONG TIME TO COLLECT

variables for function:
x = medline data file
y = article metadata file that has PMIDs


```{r}
article_metadata_citations <- GetCitationData(data, article_metadata)
```

Plot citations for each paper as a scatterplot (each dot is independent)

```{r}
PlotCitations(article_metadata_citations)
```

Bar graph of culumative citations by year
This is really the total number of citations, so not incredibly useful

```{r}
PlotCitationsBar(article_metadata_citations)
```


Testing MapPubsPerCountry function, which counts the frequency of articles published in particular countries (I believe this is country of publication NOT author affiliation. I am currently working on pulling out country info from affiliation information.)

```{r}
MapPubsPerCountry(data,article_metadata_citations)
```

